Solving two-person zero-sum sequential games via efficient computation of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker

### 2014-10-30 neurobreakfast.tex
more tex

\begin{frame}
\frametitle{Simplexes and complexes (examples of)}
\begin{figure}
  \includegraphics[width=3cm]{simplex.png}
  \includegraphics[width=3cm]{7-simplex.png}
  \includegraphics[width=3cm]{10-simplex.png}
  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
\end{figure}
\end{frame}

@@

  \uncover<2>{
    where:
   \begin{equation}
     \left .
     \begin{split}
       Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex, and}}\\
       Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
     \end{split}
      \right\}
   \end{equation}
   A saddle-point $(x^*, y^*)$ corresponds to a NE for the game.
   \item Given a fixed behavioural strategy $y_0 \in Q_2$ for Bob, a \textit{\textcolor{blue}{best-response}} behavioural strategy $x_0$ for Alice
     \footnote{Of course, there is an analogous concept for Bob.}
    is a solution to the LCP
    \begin{equation}
      \underset{x\in Q_1}{maximize}\text{ }{y_0^TAx}
    \end{equation}
}
  \end{itemize}
\end{frame}

    \begin{frame}
  \frametitle{Two-person zero sum Sequential games}
    The game tree T (from Alice's perspective) is defined as follows.
    T has a set V(T) of nodes (aka vertices) and a set E(T) of edges.
\end{frame}

>>>>

\begin{frame}
\frametitle{Simplexes and complexes (examples of)}
%% \begin{figure}
%%   \includegraphics[width=3cm]{simplex.png}
%%   \includegraphics[width=3cm]{7-simplex.png}
%%   \includegraphics[width=3cm]{10-simplex.png}
%%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
%% \end{figure}
\end{frame}

@@

    where:
   \begin{equation}
     \left .
     \begin{split}
       Q_1 &:= \{x \in \mathbb{R}_+^n\text{ }|\text{ }Ex=e\} \text{ is \textcolor{blue}{Alice's complex, and}}\\
       Q_2 &:= \{y \in \mathbb{R}_+^m\text{ }|\text{ }Fy=f\} \text{ is \textcolor{red}{Bob's complex}.}
     \end{split}
      \right\}
   \end{equation}
   A saddle-point $(x^*, y^*)$ corresponds to a NE for the game.
   \item Given a fixed behavioural strategy $y_0 \in Q_2$ for Bob, a \textit{\textcolor{blue}{best-response}} behavioural strategy $x_0$ for Alice
     \footnote{Of course, there is an analogous concept for Bob.}
    is a solution to the LCP
    \begin{equation}
      \underset{x\in Q_1}{maximize}\text{ }{y_0^TAx}
    \end{equation}
  \end{itemize}
\end{frame}

    \begin{frame}
  \frametitle{Two-person zero sum Sequential games}
  \begin{itemize}[<+->]
    \item The game tree $T$ (from Alice's perspective) is defined as follows.
    $T$ has a set $V(T)$ of nodes (aka vertices) and a set $E(T)$ of edges.
    \item Each node $v$ belongs to a single player, $p(v)$, called "\textcolor{blue}{the player to act
    at $v$}"; $p(v) := 3$ if $v$ is a leaf node. At node $v$, the player $p(v)$ has a set
    $C(v) \subset A_p$ of possible moves.
    \item For each player $p \in \{0, 1, 2\}$,
      the set of all nodes at which $p$ acts is called the nodes of $p$,
    denoted $V_p(T)$.% Thus $v(0)$, $v(1)$, and $v(2)$ form a partition of $V(T)$.
  \item There are two kinds of nodes: the \textcolor{blue}{leaf nodes} $L(T)$, at which the game must
    end and \textcolor{blue}{decision nodes} $D(T)$, at which the player to act must make a move.
    \textcolor{orange}{For example in Poker,
    a leaf node is reached at countdown, or when a player folds, or when the
    player runs out of money.}
    \item  There is a special node \textcolor{blue}{root}(T) defined by $root(T) := (/, p_0)$,

    \item In accordance with the rules of the game, every other node
      $y \in V(T)-\{root(T)\}$ is of the form $y = v.(c, p(v))$

  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Sequences and payoff matrix}
  \begin{itemize}[<+->]
    \item Let $S_p$ be the sequences of moves for player $p$. Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
      \item Precisely,
        \begin{equation}
          S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
        \end{equation}
        \item The payoff matrix $A = (a_{\sigma,\tau})$ by
          \begin{equation}
            a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
            \end{equation}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{NE computation Kuhn's Poker}
  \[   E = \left( \begin{array}{ccccccccccccc}
1&0&0&0&0&0&0&0&0&0&0&0&0\\-1&0&0&0&0&0&0&0&0&1&0&0&1\\-1&1&0&0&1&0&0&0&0&0&0&0&0\\-1&0&0&0&0&1&0&0&1&0&0&0&0\\0&-1&1&1&0&0&0&0&0&0&0&0&0\\0&0&0&0&0&-1&1&1&0&0&0&0&0\\0&0&0&0&0&0&0&0&0&-1&1&1&0
\end{array} \right),\]
  $e = (1, 0, 0, 0, 0, 0, 0)$

  %% \begin{figure}
  %%   \includegraphics[width=7cm]{Kuhn3112_NE.pdf}
  %%   \includegraphics[width=5cm]{Kuhn3112_payoff.pdf}
  %%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
  %% \end{figure}
\end{frame}
